The relative roles of genetic, ecological and environmental factors in insular species radiations

### 2018-07-04 paper/draft.tex
come up with flow for first part of intro

Island radiations like the classical Darwin finches on Galápagos or \textit{Aeonium} on the Canaries have fascinated researchers throughout history. %% cite? Darwin? ...?
However, it is often unclear why these genera produced this multitude of species as opposed to most other genera that remain species poor.
In islands, as well as continental and aquatic systems, researchers still mainly focus on environmental and ecological factors to explain speed and occurences of radiations \cite{krugSpeciesGenusRatios2008}\cite{hurlbertProcessesGeneratingLatitudinal2014}\cite{willisSpeciesDiversityScale2002}. % when radiations DID happen!
In fact, these factors often correlate strongly with the timing of genetic divergence of species and populations, % REFS!
still, in some cases the reason for maintenance of population diversity remains in the dark. \cite{chenConcordanceGeneticDiversity}

@@

Additionally, these studies highlight the cases of successful radiations, while a conclusive explanation for why these radiations could occur in the first place is still missing.

@@

@@

In this context, genetic data and analyses gain growing importance,
with an increasing number of studies also investigating genetic processes and
their effect on population variability. %EXAMPLES

>>>>

Island radiations like the classical Darwin finches on Galápagos or \textit{Aeonium} on the Canaries have fascinated researchers throughout history. %% Maybe other examples?
But why were these genera able to produce this multitude of species as opposed to most other genera that remain species poor?
For a population to produce separate species, that population must
(a) have sufficient variability in any one characteristic, e.g. traits or genome, and
(b) have reproductive barriers (e.g. environmental/geographical, ecological or behavioral) that facilitate establishment of distinct distribution patterns of said characteristic.
In islands, as well as continental and aquatic systems, researchers still mainly focus on reproductive barriers like environmental and ecological factors to explain speed and occurences of radiations \cite{krugSpeciesGenusRatios2008}\cite{hurlbertProcessesGeneratingLatitudinal2014}\cite{willisSpeciesDiversityScale2002}. % when radiations DID happen!
In fact, these factors indeed often correlate strongly with the timing of genetic divergence of species and populations. % REFS!
But even then, in some cases the reason for maintenance of population diversity remains in the dark. \cite{chenConcordanceGeneticDiversity}

@@

Additionally, these studies highlight the cases of successful radiations, while a conclusive explanation for why these population variablities and thus radiations could occur in the first place is still missing.

@@

Yet, only a fraction of them manage to radiate into multiple species through the course of their evolutionary history.

@@

A promising avenue to this with growing importance is genetic data and analyses.
Genetic analyses have already helped clearing up phylogenies of many species groups %, like bats or cichlids REFS!
and more and more complete genomes are published on a regular basis.
